NIHAO VII: Predictions for the galactic baryon budget in dwarf to Milky Way mass haloes

### 2016-08-15 ms_nihao_budget.tex
change the label of figure 4 (figure 4 in current verion)

To estimate how far the baryons escape, we measured the radius,
$\Rbar$, within which the total baryon mass equals to the fiducial
baryonic mass defined by Eq.~\ref{equ:mb}. This is a lower limit to
the true extent of the missing baryons since the baryon mass
includes gas and stars that belong to nearby lower mass haloes.
Fig.~\ref{fig:missvr} shows the baryon radius of each galaxy as
function of the virial mass.  We find the baryon radius generally
increases with virial mass. But when normalized by the virial
radius, the distance baryons are ejected to span a similar range of radii
$\Rbar/R_{200}\sim 2-6$.

%% FIGURE 4
\begin{figure}
\centerline{
  \psfig{figure=missing_vr.eps,width=0.5\textwidth}
}
\caption{Baryon radius as function of total virial mass.
         The points are colour coded by the ratio 
         between baryon radius and the virial radius of each galaxy.}
\label{fig:missvr}
\end{figure}

>>>>

To estimate how far the baryons escape, we measured the radius,
$\Rbar$, within which the total baryon mass equals to the fiducial
baryonic mass defined by Eq.~\ref{equ:mb}. This is a lower limit to
the true extent of the missing baryons since the baryon mass
includes gas and stars that belong to nearby lower mass haloes.
Fig.~\ref{fig:missvr} shows the baryon radius of each galaxy as
function of the virial mass.  We find the baryon radius generally
increases with virial mass. {\bf when normalized by the virial
radius, the distance baryons are ejected span a similar range of radii
$\Rbar/R_{200}\sim 2-6$ and gradually decrease as halo mass 
rise, even the majority of massive galaxies have $\Rbar \sim \Rvir$.}

%% FIGURE 4
\begin{figure}
\centerline{
  \psfig{figure=missing_vr.eps,width=0.5\textwidth}
}
\caption{Normalized baryon radius as function of total virial mass.
         The points are colour coded by  
         baryon radius of each galaxy.}
\label{fig:missvr}
\end{figure}
